### 2021-06-10 paper/model/testing.tex
Add tasks in red on testing in appendix.

>>>>

\textcolor{red}{

To Do für Appendix an der Stelle: Institutional details.

\begin{itemize}
    \item PCR tests only at doctor's office / test centers.
    \item Fraction PCR tests performed because of contact with infected people is small (quarantine mandate more common) -- need citation
    \item Rapid tests available in many pop up test centers, self-administered tests in every  drug store / supermarket, prices in early June < 1 Euro
\end{itemize}
}
